---
title: "File 01 - create data objects and save them in Rdata"
author: "Melinda Higgins"
date: "3/5/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Lets local some data

Let's load some data objects from the `palmerpenguins` package and the `carData` packages.

```{r}
library(palmerpenguins)
library(carData)

# load penguins dataset
# from the palmerpenguins package
ppdata <- penguins

# load American Math Society Survey Data
# dataset from the carData package
AMS <- AMSsurvey

# create sequence of numbers from -3 to 3 in steps of 0.1
# then compute the densities for a standard normal curve
# then plot the normal curve
x <- seq(from = -3, to = 3, by = 0.1)
xnorm <- dnorm(x)
plot(x, xnorm, type = "b")

```

## See list of objects created so far

```{r}
# list objects in memory created during this Rmd session
ls()
```

## Save objects to read into File 02

Let's save `AMS`, `x` and `xnorm`. We'll skip `ppdata` for now. You can always add it to the list if you like or remove the objects you don't want to save.

```{r}
save(AMS, x, xnorm,
     file = "mydata.Rdata")
```

Now open "File02_readin_data.Rmd" and read your data back in. This will work even if your Global Environment is empty. All you need is the file "mydata.Rdata".

